Reconstructing Rearrangement Phylogenies of Natural Genomes

### 2023-10-25 docs/manuscript/main.tex
changed typeface of ilp variables

\begin{itemize}
    \item Genomic marker 
    \item Genome $\X$
    \item Genome adjacency graph $\ggraph(\X) = (V, \adjacencyedges)$ \todoDany{find better name?}
    \item 
We model family assignments of marker extremities as a function $\family: \extremities \to \mathbb N$ for which holds true that for any marker $g = \{g^\et, g^\eh\}$, $\family(g^\et) = \family(g^\eh)$.  
Function 
$\minmulti_\X\varepsilon)$ reports the minimum multiplicity of the marker corresponding to extremity $\varepsilon$ in a given genome $\X$, while $\maxmulti_\X(\varepsilon)$ reports its maximum multiplicity. 
A family assignment $\family'$ is \emph{$\family$-derived} if there exists no two extremities $\varepsilon, \varepsilon'$ with $\family'(\varepsilon) = \family'(\varepsilon')$ and $\family(\varepsilon) \neq \family(\varepsilon')$.  
A family assignment $\family$ is termed \emph{$\mathcal \A$-resolved} (or simply \emph{resolved} if the context is clear) if for each member $\X$ of a set of genomes $\mathcal A$, each extremity $\varepsilon \in \extremities $ has a multiplicity not higher than $1$, \emph{i.e.}, $\maxmulti_\X(\varepsilon)\leq 1$.

    \item Multirelational diagram $\mrd$ and \emph{capping-free multi-relational diagram} (CFMRD) $\pcmrd$
\end{itemize}
\subsection{Pre-selecting Adjacencies}
\todoDany{Describe Process}
\subsection{A New ILP Formulation}
The algorithm described in the following operates on two levels: 
on the local level, a genome is derived from each genome adjacency graph, constituting a set of linear or circular chromosomes. 
On the global level, genomes are connected to each other along the branches of the phylogeny. Each branch gives rise to a pairwise comparison by means of the CFMRD. 
In doing so, the selection of adjacencies of a derived genome is propagated from across CFMRDs, thus ensuring global consistency.

\paragraph{Local level.} Constraint \ref{c:cn}

>>>>

\begin{itemize}
    \item Genomic marker 
    \item Genome $\X$
    \item Genome adjacency graph $\ggraph(\X) = (V, \adjacencyedges)$ \todoDany{find better name?}
    \item 
We model family assignments of marker extremities as a function $\family: \extremities \to \mathbb N$ for which holds true that for any marker $g = \{g^\et, g^\eh\}$, $\family(g^\et) = \family(g^\eh)$.  
Function 
$\minmulti_\X : \mathbb N \to \mathbb N$ reports the minimum multiplicity of a gene family in a given genome $\X$, while $\maxmulti_\X: \mathbb N \to \mathbb N$ reports its maximum multiplicity. 
    \item Multirelational diagram $\mrd$ and \emph{capping-free multi-relational diagram} (CFMRD) $\pcmrd$
\end{itemize}
\subsection{Pre-selecting Adjacencies}
\todoDany{Describe Process}
\subsection{A New ILP Formulation}
The algorithm described in the following operates on two levels: 
on the local level, a genome is derived from each genome adjacency graph, constituting a set of linear or circular chromosomes. 
On the global level, genomes are connected to each other along the branches of the phylogeny. Each branch gives rise to a pairwise comparison by means of the CFMRD. 
In doing so, the selection of adjacencies of a derived genome is propagated from across CFMRDs, thus ensuring global consistency.

\paragraph{Local level.} Constraint \ref{c:cn} implements the user-provided copy number constraints for each gene family $i$, where $F^A_i = \{ v \mid v \in V: v \text{ belongs to }\A\text{ and } \family(v) = i\}$ and $F^B_i$ defined analogously.
